Impact of LAIV on School Absenteeism

### 2016-08-13 paper.Rmd
new data

# Join and clean up data
students <- ab %>%
  dplyr::select(id, lunch, race, school, grade, dob) %>%
  filter(!duplicated(id)) %>%
  dplyr::rename(roster_lunch = lunch,
         roster_race = race,
         roster_school = school,
         roster_grade = grade,
         roster_dob = dob)
students <-
  left_join(x = students %>%
              mutate(id = as.character(id)),
            y = im,
            by = c('id' = 'student_id')) %>%
  mutate(consent_form_return =
           ifelse(is.na(consent_form_return), 
                  FALSE,
                  consent_form_return),
         consent_form_yes = 
           ifelse(is.na(consent_form_yes),
                  FALSE,
                  consent_form_yes),
         vaccine = 
           ifelse(is.na(vaccine),
                  FALSE,
                  vaccine)) %>%
  dplyr::select(id,
                roster_lunch,
                roster_race,
                roster_school,
                roster_grade,
                roster_dob,
                consent_form_return,
                consent_form_yes,
                vaccine) %>%
  dplyr::rename(lunch = roster_lunch,
                race = roster_race,
                school = roster_school,
                grade = roster_grade,
                dob = roster_dob)
```

>>>>

# Join and clean up data
students <- ab %>%
  dplyr::select(id, lunch, race, school, grade, dob) %>%
  filter(!duplicated(id)) %>%
  dplyr::rename(roster_lunch = lunch,
         roster_race = race,
         roster_school = school,
         roster_grade = grade,
         roster_dob = dob)
students <-
  left_join(x = students,
            y = im,
            by = 'id') %>%
  mutate(consent_form_return =
           ifelse(is.na(consent_form_return), 
                  FALSE,
                  consent_form_return),
         consent_form_yes = 
           ifelse(is.na(consent_form_yes),
                  FALSE,
                  consent_form_yes),
         vaccine = 
           ifelse(is.na(vaccine),
                  FALSE,
                  vaccine)) %>%
  dplyr::select(id,
                roster_lunch,
                roster_race,
                roster_school,
                roster_grade,
                roster_dob,
                consent_form_return,
                consent_form_yes,
                vaccine) %>%
  dplyr::rename(lunch = roster_lunch,
                race = roster_race,
                school = roster_school,
                grade = roster_grade,
                dob = roster_dob)
```
